\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{University of Queensland} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Epistasis follow-up \\[0.3cm] \huge *** summary *** \\ \horrule{2pt} \\[0.5cm] \date{}

### 2015-02-12 investigation/docs/overview.tex
figures added and scripts to make figures edited

>>>>

\begin{landscape}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & F & P & nclass & minclass & LD \\ 
  \hline
1 & 0.36 & 0.78 & 8.00 & 1.00 & 0.00 \\ 
  2 & 0.44 & 0.72 & 8.00 & 7.00 & 0.00 \\ 
  3 & 0.33 & 0.85 & 9.00 & 2.00 & 0.00 \\ 
  4 & 0.36 & 0.84 & 9.00 & 6.00 & 0.01 \\ 
  5 & 0.29 & 0.75 & 6.00 & 1.00 & 0.00 \\ 
  6 & 0.12 & 0.89 & 6.00 & 1.00 & 0.00 \\
  ... & ... & ... & ... & ...& ... \\ 
   \hline
\end{tabular}
\caption*{Header of output for a single pair}
\end{table}

\vspace{2cm}

\begin{table}[ht]
\centering
\begin{tabular}{rllllllllrlll}
  \hline
 & probename & snp1 & snp2 & nclass9 & minclass5 & LD01 & nsnpspass & nsnps & filter & lambda & nthres & nadjthres \\ 
  \hline
1 & ILMN\_1651385 & rs7989895 & rs4846085 & 419387 & 285750 & 506818 & 269121 & 506818 & 1.00 & 1.61 & 4 & 0 \\ 
  2 & ILMN\_1651705 & rs872311 & rs11032695 & 419021 & 278721 & 511121 & 260851 & 511121 & 1.00 & 1.12 & 1 & 0 \\ 
  3 & ILMN\_1651886 & rs7108734 & rs12784396 & 427787 & 319167 & 501291 & 305496 & 501291 & 1.00 & 1.07 & 0 & 0 \\ 
  4 & ILMN\_1652333 & rs898095 & rs9892064 & 442554 & 336649 & 515007 & 322786 & 515007 & 2.00 & 1.34 & 7 & 0 \\ 
  5 & ILMN\_1653205 & rs12429804 & rs2896452 & 383323 & 213815 & 507099 & 183628 & 507099 & 1.00 & 1.78 & 24 & 4 \\ 
  6 & ILMN\_1653205 & rs12454561 & rs2896452 & 386460 & 215536 & 511390 & 185098 & 511390 & 1.00 & 1.78 & 25 & 4 \\ 
  ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\ 
   \hline
\end{tabular}
\caption*{Header of summary output for 501 pairs}
\end{table}
\end{landscape}
